---
title: ""
author: "Arpan Dutta"
date: " january 22, 2024"
---

## Bivariate Normal sample generator

If we take a sample in any one of the programming language like R, the samples should be independently distributed. Can we create dependent sample from this iid sample?

Let start with a problem.

`step1`

let, $Z_1,Z_2$ \~$\mathcal{N}(0,1)$ independently

define, $X=Z_1$ and $Y$ $=$ $\rho Z_1 + \sqrt(1-\rho^2)Z_2$ where, $\rho\in(-1,1)$

then we can say that,

1.  $X,Y$ \~ $\mathcal{N}(0,1)$ marginally

2.  $\rho(X,Y)=\rho$

3.  more preciously, $X$ and $Y$ jointly follows $\mathcal{N}_2(0,0,1,1,\rho)$

`step 2`

Let, $X$ \~ $\mathcal{N}(0,1)$

Define $Z= X\sigma+\mu$ where, $\mu\in\mathcal{R},\sigma>0$

Then, $Z$ \~ $\mathcal{N}(\mu,\sigma^2)$

`step 3`

let, $Z_1,Z_2$ \~$\mathcal{N}(0,1)$

Define $X= Z_1\sigma_1+\mu_1$ where, $\mu_1\in\mathcal{R},\sigma_1>0$

Define $Y= Z_2\sigma_2+\mu_2$ where, $\mu_2\in\mathcal{R},\sigma_2>0$

then we can say that,

1.  $X,Y$ \~ $\mathcal{N}(0,1)$ marginally

2.  $\rho(X,Y)=\rho$

3.  more preciously, $X$ and $Y$ jointly follows $\mathcal{N}_2(\mu_1,\mu_2,\sigma_1^2,\sigma_2^2,\rho)$

Thats it

```{r,filename = 'Bivariate Normal sample generator'}


BVN<-function(size,mu1=0,mu2=0,sd1=1,sd2=1,rho=0){
  stopifnot(exprs = {
    sd1>0
    sd2>0
    -1<=rho 
    rho<=1} ,local = TRUE)
  
  z<-rnorm(n=2*size)
  sample.mat<-matrix(z,ncol=2)
  std.y<-apply(sample.mat,1,simplify = TRUE ,FUN = function(z){
    y<-(rho*z[1])+(sqrt(1-rho)*z[2])
    return(y)
    })

  x<-mu1+(sample.mat[,1]*sd1)
  y<-mu2+(std.y*sd2)

cbind(x,y)}



```

ploting a random sample from my function.

```{r}
sam<-BVN(size=500,rho=-0.73,mu1=0.5,mu2=1.8,sd2=sqrt(2))

plot(sam,pch=20,col='lightgreen')
```
