---
title: "Real-estate"
author: 
 - Arpan Dutta
 - Soumyajit Roy
 - Sourav Biswas
format: html
execute: 
  echo: true
editor: visual
---

## Packages

```{r,filename='Used packages'}
library(ggplot2)

```

## Data: real-estate {.scrollable}

<font size="4.8">

| Variable        | Description                                             |
|-----------------|---------------------------------------------------------|
| Price           | Sales price of residence (dollars)                      |
| Sqft            | Finished area of residence (square feet)                |
| Bedroom         | Total number of bedrooms in residence                   |
| Bathroom        | Total number of bathrooms in residence                  |
| Airconditioning | 1= Presence of air conditioning, 0= otherwise           |
| Garage          | Number of cars that garage will hold                    |
| Pool            | 1= Presence of Pool, 0= otherwise                       |
| YearBuild       | year of construction                                    |
| Quality         | 1= high quality, 2 = medium, 3 = low                    |
| Lot             | Lot size (square feet)                                  |
| AdjHighway      | 1 if the property is adjacent to a highway, 0 otherwise |

</font>

## Structure of the Data

```{r}
real<-read.csv("C:\\Users\\arpan\\Documents\\data\\real-estate.csv")
real<-real[,-1] #---removing ID
for(i in c(5,7,9,11))real[,i]<-as.factor(real[,i])
str(real)



```

## Full model

```{r}

fm<-lm(Price~.,data=real)
summary(fm)
```

## olderhouse tends to lower price?

```{r}
ggplot(data=real,aes(x=YearBuild,y=Price))+
geom_point(col='tomato')+ labs(caption='Data=real-estate')


```

## How much adjancey to highway affects the price.

```{r}

ggplot(data=real,aes(x=AdjHighway,y=Price,colour=AdjHighway))+
geom_boxplot()+ labs(caption='Data=real-estate')


```

## Age?

```{r}


g<-ggplot(data=real,aes(x=YearBuild,y=Price,colour=AdjHighway))+
  geom_point()+
  labs(caption='Data=real-estate',title='Price with Age') 
g

```

## Price vs Sqft with Quality

```{r}
#---plot | Quality
ggplot(data=real,aes(x=Sqft,y=Price,colour=Quality))+
geom_point()+ labs(caption='Data=real-estate',title='Scatterplot with Quality')

```

## Price: Airconditioning vs Non Airconditioning

```{r}

ggplot(data=real,aes(x=Airconditioning,y=Price,colour=Airconditioning))+
geom_boxplot()+ labs(caption='Data=real-estate')

```

## Testing

```{r}
ac<-real$Price[real$Airconditioning=='1']
nonac<-real$Price[real$Airconditioning=='0']
t.test(ac,nonac,var.equal = TRUE,alternative='greater')
```

## Model Assumptions of the Full Model

-   Errors have mean zero.

-   Errors are Homoscedastic.

-   Errors are uncorrelated.

-   Errors are Normally distributed.

## Residual vs Fitted

```{r}
residuals<-residuals(fm)
fitted<-fitted.values(fm)
ggplot()+geom_point(aes(x=fitted,y=residuals),col='tomato')+
  geom_hline(yintercept = 0,col='navy')
```

## Normality Checking

```{r}

ggplot()+stat_qq(aes(sample=residuals),col='tomato')+
  stat_qq_line( aes(sample=residuals),col='navy')
```
